\chapter{April}
Tuesday was a busy day. This evening will be my most adventurous casting session, yet. I
made sure that the camera was loaded and ready, then went to setting my supplies out on my cart.
Of course, I laid out a bit more than what I actually calculated that I would need, but it's
always better to have too much, than to be running to the closet while a cast is drying on a
model. When I finished, the cart was piled high, and I was ready.

April had looked very beautiful the night I interviewed her. She had been wearing a sweatshirt,
and jeans, and I could tell that she had a figure that begged to be casted. When she arrived
Tuesday evening, in shorts and a midriff top, I saw that my initial impression had been an
understatement. She could certainly have been a professional model, and in a much more
mainstream manner than what we were to be doing that evening. I led her inside, and had her sit
in the parlor, while I retrieved the envelope with the cash.

``April, I certainly appreciate your willingness to change the plans on such short notice.
Saturday night, my patron saw something that caught his interest, and he wanted me to do
something more along those lines.''

``That's not really a problem. It's a bit scary, not being able to move around much, but the
extra money will sure be nice.'' She replied.

``Speaking of the money, here it is. I always make sure that payment precedes performance,'' I
said, handing her the envelope.

She opened the envelope, discretely counted the money, then folded the envelope in half and
placed in the small overnight bag she had brought.

``I need a few minutes to change, where can I do that?'' She asked.

``Right through that door there,'' I said. ``I have one last-minute thing to do, and I'll be
ready. I'll be back in just a few minutes,'' was my answer.

She disappeared into the casting room, and I went to the kitchen to fill my casting bucket with
water.

I returned to the casting room, and tapped on the door before I entered.

``Come on in, I'm ready.''

When I entered, she had changed into what she had promised: a black, string bikini, which made
her look even more beautiful.

I placed the bucket of water with my cart, and led her to the casting table. I had her stand
next to the table, and pushed my cart to her side. I had her raise her arms, and I slipped a
length of eight-inch stockinette over her arms and body. I pulled it down to her knees.

I then made a downward cut about four inches long in the top of the stockinette under each arm.
Next, I took two cut broom handles, which I had readied earlier. I told her that she could use
them to support her arms, while she held them out to the side for me. After she had done this, I
pulled the stockinette up so the bottoms of the cuts were against her armpits. I then lapped the
flaps over her shoulders, and taped them down. I finished the stockinette by wrapping a section
of four-inch stockinette over her torso in a figure-eight style so that the stockinette laid
down around her breasts. I wanted this cast to accentuate her wonderful curves, not lessen them.

With this done, it was time for padding. I had to be careful, as this cast could easily become
uncomfortable if it were not padded correctly. After asking April if she was okay, took a roll
of six-inch padding, and began at her hips, working my way up. I made the padding three layers
thick, with an extra layer over her hipbones, for comfort. I began a second six-inch roll of
padding, and when I had wrapped up her torso, to her armpits, I tore off the remainder. I then
took a roll of four-inch padding, and worked it in the same figure eight manner as the
stockinette, covering her shoulders, and molding the padding to her figure.

``We're ready for the fiberglass, now. How are you doing?'' I asked her as I slipped on my
gloves.

``It feels fine so far. Like wearing tight clothes.''

``Well, it's about to feel very strange. You'll feel some pressure as I wrap the fiberglass
tape. Not heavy pressure- in fact, it will almost feel distant through the padding. As the
fiberglass starts to set, you'll feel heat, but nothing unbearable. The padding will insulate
you from it.''

``I'm ready.''

I tore open the foil wrapper on the first roll of five inch purple fiberglass. I wrapped it in
the same manner as the padding, starting too low on the hips, but I planned to trim the cast
after it had dried. I wrapped four rolls of five-inch fiber on her stomach and lower back, but
stopped just below the breasts. I then started with four inch purple fiberglass, and returned to
my figure-eight pattern.

After her entire torso was covered with purple fiberglass, I took a break. I asked her if she
needed anything to drink. She asked for water, so I got some, took the broom handle she held
with her right hand, handed her the glass of water and told her to be careful not to touch the
drying fiberglass with her arm.

``Why?''

``It is still setting. It is very hard to get off of skin, and it can irritate you pretty badly
.I don't want you itching, especially since it is going to be so hard to scratch.''

While she sipped her water, I picked up some of the mess that had accumulated so far, as there
was going to be more before we finished.

After the mess was picked up, I felt of her cast to see if it was set. It had become quite hard,
so I retrieved my cast saw.

``Let me trim this a bit, then we can finish it up, and you can sit down.''

I took the water glass from her, handed the broom handle back to her, and began to trim the cast
at her hips. I trimmed the cast so that it held her spine perfectly straight, but barely allowed
her to raise her legs perpendicular to her body. I then trimmed the cast a bit at the neck and
shoulders, smoothing out the edges, and making room to allow her arms to move fully. I then
pulled on a fresh pair of gloves, (the old ones were probably rock hard by now) folded back the
stockinette, and anchored the padding around her hips, neck, and shoulders.

Finally, there she sat, a beautiful woman, cast in a body cast that was, being honest, nicely
made. For a first attempt at a body cast, I was pleasantly surprised at how well it had turned
out.

``April, we need to let that cast set up for a little while longer before we go on. Does it feel
comfortable to you.''

``Yes, it's not uncomfortable at all. It feels like it isn't as warm inside as it was.''

``Good, that means it's almost set. In a few minutes, I'll let you get up and move around a bit
if you like.''

``I'd like to try using the rest room, if you think I can.''

``That might be tricky, but you should be alright.'' I was a bit worried about this- how would
she do at getting down, and then back up? I could, of course, help her, but that would be
uncomfortable to her, no doubt. I thought about it a few moments until an idea came to me. I
went and retrieved the aluminum crutches from the closet.

``Here. When you go, take these with you. You won't need them to walk, but you might need them
getting up and down in the bathroom. I'll stick close by the door, so if you need my help, just
call out. But if you don't, you can still have your privacy.''

``Thank you very much,'' she replied.

The bathroom trip went without incident. I helped her with the first few steps until she had
adjusted to walking without being able to flex her spine. I followed her to the rest room, and
waited while she was inside. I heard her shuffling to get down, and then I heard more shuffling
as she got back up, but she did it on her own, and thankfully didn't need my help.

As she emerged, she handed me the crutches. I noticed that her bikini bottom was now on the
outside of the cast. It seemed to make the whole thing look more realistic to me

``I'm ready to finish, now.'' She said.

I led her back to the casting room, and helped her sit on the table. I slipped three-inch
stockinette on her left arm all the way up to her shoulder, then cut it off just past her
fingertips. After making a slit and pulling her thumb through it, I wrapped her hand, wrist and
most of her forearm with two inch padding, and finished by using most of a roll of three inch
padding to wrap the arm all the way to her armpit.

I instructed April to hold her arm out away from the body cast, with the elbow slightly bent.
Most long arm casts have a ninety-degree bend at the elbow, but I have seen a few that were
almost straight, and I always liked the look. I suppose I like it because the arm is not nearly
as useful when it is casted in this manner.

I took one of the rolls of three inch purple fiberglass, and asked April if she were ready to
continue.

``Yes, I'm fine. In fact, it's really interesting, watching you work. It's also very weird to
experience it from the inside. It's like, one minute, I'm flexible and fine, but next thing I
know, I'm stuck.''

``So you're not getting claustrophobic or anything like that?'' I asked her.

``No, I'm really fine with this.''

I smiled and returned to my work. I dipped the first roll of three-inch fiberglass and started
wrapping it at her armpit. I worked down her arm until the roll ran out near her wrist. I folded
over the padding at the top of the cast, and anchored it with a second roll of fiberglass.

I then began using two inch purple fiber to wrap her forearm, wrist and hand, folding the roll
in the ``Z'' pattern between the forefinger and thumb. One roll built strength and thickness,
then I folded over the end and anchored it with a second roll.

``That arm is done,'' I announced. ``Ready for the other one?''

``Yes,'' she said, holding out her right arm.

I slipped more of the three-inch stockinette on her right arm, this time going only past the
elbow. I cut the thumbhole, and then wrapped her hand, wrist and forearm with a roll of two-inch
padding. One roll of three-inch fiberglass made an excellent base for the cast, and a second
roll anchored the padding and stockinette.

I stepped back and admired my work thus far. On my casting table was a beautiful blonde in a
long arm cast, a short arm cast, and a body jacket cast, All in purple fiberglass. Not exactly
what I had seen on the woman at the car show, but definitely inspired by her. One more thing to
do, and it will be perfect.

``April, we're down to one last cast to make.''

She scratched her nose with her freshly casted right hand, and smiled.

``I'm ready whenever you are. Which leg do you want?''

``Left,'' I said, moving the footstool over to where she sat.

She held out her left leg, and I slipped four-inch stockinette up to the top of her thigh. I
made sure to bunch it at the top slightly, as I planned for this cast to go up very high on the
leg. I grabbed a roll of 4 inch padding, and worked my way down from the top, so as to smooth
out the bunches in the padding with the next layer. Two and a half rolls of padding later, I had
fully covered her leg with 2 layers of padding, with a third layer at the ankle and knee.

``Are you still comfortable? No problems with going on?'' I asked.

``I'm fine. It's really kind of interesting, trying to move in these things. I'm sort of trying
to move my wrists, and my arm, and there's very little movement inside these casts. It's also
sort of wild, feeling the weight of the casts on me.''

``Well, then- lets finish this up.'' I said, pulling on another pair of gloves.

I took a roll of five inch purple fiberglass, dipped it, and began to wrap at the top of her
leg. I overlapped each turn of fiber by one half over the one before. I laid a second roll
directly over the first, making four layers on her thigh and knee. I folded over the padding and
stockinette at the top, and used a third roll to anchor it and give thickness to the top of the
cast. I then switched to four-inch fiberglass, and started just above the knee, working my way
down. Another roll directly over it, and I was done except for her foot. I took another roll of
four-inch fiber, and started at the ankle, working down to her toes, then back up to the rest of
the cast. I then folded over the padding, and anchored it with a fourth roll of four-inch
fiberglass. I added one more roll to the foot, ankle and lower leg areas to make certain that
the cast was good and strong, and my greatest work to date was complete!

``April, we're done casting. How does it all feel?''

``It feels okay, really.'' She answered. ``I sure wouldn't want to be like this for very long,
though.'' She added.

``It won't be long before we get you out. We can go do the sketch in a short while. Would you
like something to drink?''

``Yes, I'm getting thirsty.''

I went to the kitchen, and got sodas for each of us. I left mine in the can, but I poured hers
into a mug, so she could easily hold it with a casted hand. I also put a straw in it, so she
could drink without leaning back. As I returned with the drinks, she began to ask me questions.

``So, how did you come to do this? I mean, you don't see many ads in the paper for artists to
put casts on women, then draw pictures of them.''

``No, you don't,'' I replied. ``Let's just say I was in the right place at the right time.''

April wasn't letting go of the questions, though.

``So you get paid well for this?''

``Yes, I am well taken care of.''

``And this is what you want to keep doing with your life?''

She was really grilling me. It wasn't in any sort of flirtatious way, she was just being
curious. I finally ducked out of her questions by announcing that we were ready to move to the
other room.

I helped April to stand up and turn to her side. I then helped her to sit down in the
wheelchair. I placed the footrest under her casted left leg, and wheeled her into the parlor. I
retrieved my camera, and started taking pictures of her sitting in the wheelchair. I then helped
her from the chair to the sofa, and took some more photos.

Finally, I moved a table over to the French doors, and helped her to stand up and lean against
the table. Bathed in the sunlight, it was a beautiful place to sketch her. I asked if she
thought she could stand that way for a short time. She said that she could, and ran her casted
right hand through her hair. That was it. Perfect. I asked her to put her hand back to her head,
and I began to draw.

I worked quickly, as I was worried about her losing her balance and falling. The drawing took
shape very well, capturing her beauty, as well as her helplessness in the casts. After the
sketch was done, I helped her back to the wheelchair, and took her back to the casting room.

Once back in the casting room, I retrieved my removal equipment: cast saw, bandage scissors, and
cast spreaders.

``Which cast do you want out of first?''

``The body cast, please. It's starting to hurt my hips a little bit.''

``Absolutely. I see you looking at the saw sort of strangely. Let me show you how safe it is.''

I turned the saw on, and held the oscillating blade to my bare hand. I then showed her that the
cast did not cut my skin.

``This saw only cuts hard objects. Anything soft, it just vibrates on.'' I could see the relief
in her eyes, so I instructed her to lie down, and helped her to do so.

I quickly cut through each ``strap'' over her shoulders, then raised her arms above her head,
and cut each side from armpit to hip. I pried the cast apart a bit with the spreaders, and then
cut through the padding and stockinette down one side with the bandage scissors, making sure not
to cut the straps of her bikini top.

I then placed her arms back at her sides, and cut through the padding and stockinette over each
shoulder. I then opened the cast, almost like a book, and helped her to sit up, freed from the
fiberglass. I noticed that the stockinette had imprinted its pattern on her skin.

I quickly cut each of arm casts in a similar fashion: cutting through the cast on both sides,
but only through the soft material underneath on one side, allowing the casts to open like a
book. I removed the leg cast by cutting down the side, going under her heel, then back up the
opposite side with one long cut. Once the padding and stockinette was cut on one side, I was
able to open the cast, and removed her leg and foot from the back, leaving the entire foot area
of the cast intact.

Once free, April put her clothes and shoes back on. Before she left, we thanked each other, and
I left her with an open invitation to call if she ever wanted to work with me again. She said
that she might, and left.

Once she was gone, I gathered the cutoff casts, and placed them in the basement with then
others. My collection was growing. As I returned upstairs to clean up the casting room, I
wondered if I was becoming addicted to this. Was it going to take more and more to satisfy me?
Is it going to take more and bigger casts? If it is, is it such a bad thing?
