\chapter{}
``Hello, Monique,'' I said with little attempt at a pleasant tone of voice.

``Hi, Quinn- how is the... Art coming?''

How nice- small talk. I suppose I should act surprised when she asks for something. ``It's
doing just fine, why do you ask?''

``So, you're overloaded with models to put casts on, then?''

``Not really, actually. The town seems to have cleared out for the summer.''

\begin{thought}
He sure doesn't sound like he's happy to hear from me. Maybe this was a mistake. No- it
can't be. I need to make some money, or I'm going to lose the apartment. With things being slow
for the summer, I can't get enough hours at work to keep up. Brace yourself, ask him, but keep
your dignity about it.
\end{thought}

``If you'd like, I'd be willing to work with you again.''

There it is. That's what she wants. No- no way. I drew a breath to blow her off, hopefully
for good, then caught myself. Okay- so she's a cash hound. She has no redeeming qualities past
her looks, but she CAN make a cast look very good, and it would appear she doesn't find the
thought of being casted totally repulsive. Besides, I've had some new ideas recently, and am
looking forward to trying them out.

``Quinn, are you still there?''

``Yes, just thinking for a moment. I'll have to check to see if it's OK, but he liked what we
did the first time, so I guess it's possible.''

``Great! What sort of cast will I wear this time? Or more than one again?''

``I don't know, yet. I'm not promising we will. I just said I'd check. I'll have to call,
leave a message, and wait for him to contact me. Call me in a couple of days, OK?''

``Sounds good to me, I'll talk to you soon.''

\begin{thought}
Hmm- this sounds promising. I know I can't get my hopes up too much, but it's hard not to.
I'll keep my fingers crossed and just keep hoping for the best.
\end{thought}

After I hung up the phone, a wicked thought passed through my mind. Since I don't have much
respect for her, I guess I could try a few things with Monique that I'd be a bit nervous to try
with someone new. Nothing immoral or illegal, but maybe get her outside while casted, or maybe
more elaborate casts. Maybe keep her in the casts a bit longer than the others. I drifted off in
my thoughts, deciding to make sure that I got the most for my money with Monique.

\begin{thought}
Monique was anxious the day she was to call, and she wasn't exactly certain why. Sure, she
needed the money, but was that really all? She knew it wasn't. Was there part of her that wanted
to see Quinn again? She thought there might be, but she wasn't sure. Then there were the casts.
She remembered the casts feeling much different than what she had expected. Almost comfortable.
That seems so weird- wearing a cast always looked like such an inconvenience. She wasn't sure
which of these feelings was the strongest. She just knew she had to make the call.
\end{thought}

``Hello?''

``Hi, Quinn, it's Monique. Do you have news, yet?''

``Yes, we are approved. I guess he wants to see you casted again.''

``Great! So what is the exact plan?'' She asked.

``Actually, he gave me a few suggestions, and I haven't decided yet on which one I want to
do. If you want, you can come over Saturday. We'll talk it over, and decide which one, and then
go ahead and do it.''

``Sounds alright to me,'' she said with a note of apprehension, ``Should I wear the same thing
as last time?''

I thought for a moment about this. I wanted to do more this time. Time to surprise her a
bit.

``Monique, we're going to do things a little differently this time.''

\begin{thought}
``Uh-oh,'' thought Monique. ``I hope he doesn't want me naked. I understand the artistic value
of nude models, but I won't do it. It just seems wrong to me.''
\end{thought}

``Different in what way?'' She asked.

``Different in that we're going to be a bit more adventurous.''

\begin{thought}
Oh boy. Here it comes.
\end{thought}

``This time, you'll be in the casts a while longer. Also, some of the photos will be taken
outside.''

``Outside?'' she asked. ``In public?''

``No, I don't think in public would be a good idea. Maybe just in the back yard, by the pool.
I have a privacy fence, so nobody will see you.''

``Oh, OK'' she replied. ``In public could be difficult to explain the next day when I was back
to normal, with no cast on.''

``Yes,'' I answered. ``I don't want that to happen. Some people around here would find what I
do to be a bit too bizarre.''

``I guess so, but it's not bad, really. I'd hate to have to wear a cast for months, but for a
little while, it's actually kind of cool.''

Her last statement hit me like a ton of bricks. She said it was ``kind of cool.'' She didn't
actually ENJOY her casts, did she? Is she really doing this just for the money? Maybe she just
thinks it's kind of cool to not have to really work to make money. Oh well, let's hit her with
the next bomb, and see how cool she thinks THAT is.

``Monique, as far as what you should wear- you'll need a bra or bikini top with good support.
Maybe a push- up, if you have one. For the bottom, a bikini or some shorts will be fine for the
type of cast we'll be doing.''

``What kind of cast is that?'' she asked.

Here comes the bomb- ``We're going to do a body cast.''

A slight trace of worry in her voice with her response: ``You mean, a cast from my head to my
toes?''

``No, not a full body cast,'' I replied. What we'll do is a cast known as a plaster vest.
You'll essentially only have your torso casted. Maybe we'll do an arm or a leg, as well. You'll
still be able to move around somewhat. Since this will be more intense than before, you'll be
paid more money.''

\begin{thought}
Monique's mind was wandering as she remembered the feeling of the warm, heavy plaster
setting on her arm and leg. She remembered the restraint of the casts after they had set. She
tried to imagine what that would feel like over her body. She felt a flush of heat inside her at
the thought. Could this thought actually be exciting her? ``Get a hold of yourself! Stay calm
and...''
\end{thought}

``Monique? Are you there?'' I asked, breaking the silence.

Snapped from her thoughts, she searched for something to say.

``Yes, I'm still here.'' Quick- say something so he doesn't figure out how this idea makes you
feel! ``How much more money?''

Ah, there is the Monique I know and hate. Always thinking about the dollars.

``At least a hundred dollars more, depending on whether we do more than just the body cast.
Of course, if you don't feel comfortable with wearing such a big cast, we can forget the whole
thing.''

``No, no.'' said Monique, maybe still slightly flustered in her thoughts. ``It sounds
intriguing to me.''

``Great, then. I'll see you Saturday morning at 11:00 am, if that's OK with you?''

``I'll see you then. Goodbye.'' She hurriedly said, and hung up.

\begin{thought}
``You sure made a fool of yourself!'' Monique thought to herself. ``You sounded like an idiotic
schoolgirl with a crush! Intriguing? Why did you say that? What's the point of trying to be a
strong person if you're going to say shit like that, and throw it all out the window?''
Disgusted
with her perceived weakness, Monique turned on the television to forget about it.
\end{thought}

``She said 'intriguing,''' I recalled to myself. ``She said it sounded intriguing. She also had
said her long arm and long leg casts were ‘actually kind of cool.' Is it possible that she
actually enjoys this?'' My cynical side responded by reminding me that she asked about the
money,
too. She's definitely a strange one. First, she comes across as a materialistic cash-hound, but
the last couple of times I have talked to her, she shows signs of mellowing out some. I just
don't know about her. I decided to straighten up the cast room and get ready, hoping to be able
to get my mind off of it.

\begin{thought}
There was nothing on television interesting enough to take Monique's mind off of the thought
of wearing a body cast. She kept thinking about how the plaster had felt around her arm and leg.
The warmth and the weight as it set, and the snugness and restriction of it once it had dried.
She closed her eyes, and imagines Quinn putting her whole upper body in a cast. She pictured his
hands, wrapping and smoothing the plaster over her stomach and breasts. Once again, she felt a
wave of heat pass through her body. ``Monique, there's no denying the truth- you're looking
forward to this. You want to wear this cast, and you want Quinn to put it on you!'' This
admission to herself caused mixed emotions: admitting the desire and realizing why she felt so
strange when she talked to Quinn was settling, but knowing that the situation had a level of
control over her was very disturbing. ``You shouldn't do it'' she told herself, ``anything that
causes you to give up one iota of control over yourself can not be healthy. Once you give anyone
else any power over you, you are asking to be hurt.'' She finally resigned herself not to go
through with it. Sure, she would regret not having done it, and she did need the money, but
nothing was worth making yourself vulnerable over. She resolved to call him tomorrow morning,
and back out. Still lying on the couch, she drifted off to a restless sleep full of confusing
dreams: She saw herself, with Quinn, on a beach. She was wearing a body cast from her shoulders
to her hips. She and Quinn were joking, and smiling, and seemed to be enjoying themselves. Later
in the dream, Quinn was putting casts on her legs. Both legs, from her toes up to her hips.
Somehow, she knew in the way you know in dreams, that Quinn was doing this not as a job, and not
as an artist. He was doing it simply because he enjoyed it. She found the dreams to be pleasant
and enjoyable. Other dreams followed, and in all of them, she was wearing a cast, or having one
applied. Quinn was a constant through the dreams, too. Also, she found the contented and happy
feeling to be constant.

When she woke, she knew there was no way she was going to call and back out. She was going
to go see Quinn, and she was going to get her body cast, and she was going to enjoy it. She also
knew she was going to do something that might surprise him a bit, too.
\end{thought}
