\chapter{}
Monday morning at 9:00, Erin crutched up my sidewalk looking great. She wore denim shorts,
red T-shirt, and a sandal on her right foot. Over her shoulder was a small overnight bag, no
doubt with part of her wardrobe for the session. Of course, the rest of it, I would be
providing. I met her at the door.

She smiled. ``Well, here I am, ready to go, I think.''

``Great. Come on in and we'll get started,'' I said, trying to hide my excitement. ``May I
take that bag for you?''

``That's OK, I've got it,'' she said, not trying to hide annoyance. ``My leg is broken, not
my arm.'' Sort of a bitchy answer, but she probably was getting sick of being treated like an
invalid.

I led her to the casting room, where I had everything ready. I asked her to have a seat for
a few minutes before we started.

``Erin, I'm really glad you have decided to try this. I spoke to the ‘Boss,' if you will,
and he's eager to see what sort of work you and I can turn out.''

``Well, it sounds like my part will be pretty easy- just sort of sit back and let things
happen,'' she said.

``For the most part, yes.'' I told her. ``But your attitude can really show through in the
work, too. It will affect the final work.''

She smiled again. ``I won't let you down.''

``I'm sure you won't.'' I thought to myself.

``For today, Erin, I don't want to do anything overwhelming. I'd just like to do a quick
shoot here at the studio. We're not going to cast you too heavily, either. I think for your
first time, we'll just put a cast on your right leg like the one you already have.''

``Sounds fine to me,'' she replied.

``Did you bring tasteful lingerie, like I asked?''

She nodded, and opened up her bag. She removed the items one at a time and my mind raced as
I saw each item and pictured her in it. When the bag was empty, she asked which one I liked the
best. I honestly could not decide- I wanted to see her in all of them.

After a quick moment of thought, I told her ``How about you wear whatever you're most
comfortable in?''

Now it was her turn to think for a moment. ``I think that would be these,'' she said,
holding up the simple dark blue camisole set.

``OK, I'll leave you to change. But first, your pay for today will be \$350.00, and we
should be done by 1:00 p.m. I handed her the envelope, and left her to change.

Out of the casting room, I went into the ``hospital room'' which still smelled of the white
paint I had finished the day before. I retrieved the wheelchair, then went and filled my bucket
with warm water. I was nervous, and I knew why: All of the women I had casted were very
attractive, but Erin was different. Maybe it was her cast, but I didn't think that was it. There
was something more than the cast, and her beauty that was pulling at me. I decided to smoke a
cigarette to calm myself. She might need a few extra minutes to change, anyway, considering she
had to fight with a long leg cast.

I returned to the casting room and tapped lightly on the door. ``Are you ready?''

``Yeah. Come on in.''

I went inside, and was very pleased at the sight I beheld. She sat on the casting table, and
in the dark blue lingerie and hot pink cast, she looked fantastic. Once again, I had to remind
myself to stick to the program, and appear professional.

``Well, it looks like you're ready to start, so let's begin.''

``Ready as I'll ever be, go ahead,'' she replied.

I took the roll of 4'' wide stockinette, and unrolled what I knew from experience to be more
than enough. I slid it up her right leg to her upper thigh. I didn't go quite as high as I would
have liked, because I wanted the cast on this leg to match the other one. I then started the
padding from the top and worked down, smoothing out the bunches in the padding as I made each
turn.

``So, am I doing it the same way as the pros?'' I asked, trying to make some conversation.

``I really don't remember when they put the cast on,'' she said. ``They had me pumped full
of Demerol, and by the time they put the cast on, I was pretty well out of it.''

I gave her an understanding nod as I ripped open the first roll of 4'' pink fiberglass.
Working in the same downward motion, I had used six rolls of fiber before the cast was finished.
I pulled off my gloves.

``There' we'll give that a few minutes to set before we go into the other room,'' I engaged
her in some small talk, just trying to make conversation, to pass the time. She was polite, but
didn't seem too eager to talk about herself- her job her friends (never mentioned a boyfriend, I
noticed) or her injury. Her broken leg disgusted her, and by the way she looked at it, she
wasn't too happy about her new cast, either. Hopefully, she would warm up to it, even if only a
little.

When more than enough time had passed for the cast to set, I told her that it was time to
move to the other room. She reached for her crutches, then looked at me: ``Will this work?'' She
asked.

``Probably not, I have an easier way.'' I stepped out of the room, and pushed the wheelchair
inside.

``Here, grab around my neck.'' She did, and I lifted her up and placed her gently in the
wheelchair. I must tell you, that was a pretty intense experience for me- a definite dream come
true. I was helping an extremely attractive woman in two leg casts get into a wheelchair, it was
almost hard to believe. I adjusted the leg rests to accommodate her legs, and pushed her into
the ``hospital room.''

I took a few photos of her in the wheelchair. She put on a nice smile, and looked wonderful,
but the smile seemed very ``pasted on'' to me. I really wished she had been a little more into
the photos.

I helped her onto the bed (Wonderful again), and took some photos of her from various
angles. Once I was ready to do the sketch, I had the idea for her to close her eyes, and act as
though she were asleep. With her eyes closed, I felt a little freer to admire her beauty as my
pencil worked over the paper. It almost amazed me, watching her image take shape on the page in
front of me.

When I was done, I said ``There- all done,'' and showed her the drawing.

``Wow, that really looks like me!'' she said.

``Thank you. Are you ready to get out?''

``Yes!'' She said, a little too eager for my taste.

``OK, back to the other room.''

I picked her up from the bed and placed her into the wheelchair once again, then back onto
the casting table once we were back in the casting room. I remember thinking to myself that I
could really get used to it.

Once back on the table, I took the cast saw and carefully cut down the sides of the cast on
her right leg. When the cuts were done, I used my bandage scissors to cut the padding \&
stockinette on the outside of the leg. The cast opened up, and Erin pulled her leg out.

``I don't suppose I could talk you into doing that to this one could I?'' she said, tapping
the cast on her left leg.

``No, and you really don't want that anyway,'' I replied. ``As much of a pain as it is, that
cast is your leg's best friend right now.''

``Yeah, yeah- I know, but it's hard to remember that sometimes. Have you ever had to wear a
cast?'' She asked, reaching for her shirt and shorts.

``No, I told her. Of course, I had casted myself several times, but had never been forced to
wear one for an extended period of time. I could easily understand the inconvenience of having
to wear one for weeks.

``Well, let me tell you, it's no picnic.''

``I can imagine so. Let me get out of here while you dress.''

``That's OK, I'll just put my clothes on over these,'' she said, bending to get her shorts
over her casted left foot. Watching her dress, I knew I had to make some sort of conversation,
even if it was lame. Otherwise, I would simply be ogling her, and I didn't want to scare her
away.

``So, what do you think of the modeling job?'' I asked.

``It's really weird.'' She replied.

I was a bit dismayed. ``So, do I need to find a new model for Mondays?''

``No, I don't think so. It's weird, but it pays well, and I don't see anything wrong with
it,'' She said as she pulled on her T-shirt, and bent to put her sandal back on her right foot.
She hopped down on her right leg, and grabbed her crutches. With a smile she added, ``As long as
I'm still welcome, I'll be back next week.''

``I'm sure you will be.''

``Then I'll se you next Monday at 9:00?''

``I'll be looking forward to it,'' I said before realizing how it sounded.

She looked at me a bit oddly as she crutched past me to the front door and let herself out
before I could open the door for her. I peered out the window as she hobbled down the walk,
lowered herself into her car and drove off.

Amazing woman.
