\chapter{}
``Hi, I'm Erin.'' Said the girl in the long leg cast.

My heart was pounding. I've seen some very attractive women around this town, and I've had
the good fortune to see several of them in casts, by my own hand. But something was different
with this one. I wasn't sure if it was her cast, or her breathtaking beauty that was affecting
me that way. Another part of my mind found humor in the irony- I was seeking women to cast, and
this one comes with a cast of her own.

``Come inside, Erin,'' I said. I led her to the parlor, and pointed to the couch and asked
her to have a seat. Thinking of her leg, I excused myself long enough to retrieve one of my
stands from the casting room. I made these stands to support a leg during the casting process,
it should help her be more comfortable.

``Here, try this for the leg,'' I told her and she hoisted her leg into the cradle. It was
very exciting, to watch her managing with her leg being stiff and heavy, and I could have easily
lost myself in that moment, but I forced myself to remain professional.

``Comfortable?'' I asked.

``Yes, I have no idea what this thing is, but it works great for sitting down with this
cast.''


``So, what happened to your leg?'' I asked.

``Well, I was doing some painting in my apartment, and I leaned a little too far on the
ladder and fell. When I came down, I landed off balance on my leg, and I heard a snap. They
showed me the picture of my leg, it broke right about here.'' She made a motion with her hand
about 4 inches up from her ankle. ``So now, I'm stuck in this cast, and I guess I should have
told you before I came. If this modeling isn't from the waist up, you have no use for a woman
with a broken leg.''

``Erin, your leg does not exclude you from this job. In fact, it is a benefit. Remember when
I said you'd need an open mind for this job?''

``Yes,'' she said, with obvious unease in her voice.

I decided to cut to the chase. A cast fetish will probably disgust her, since she is forced
to wear a cast for weeks, and it's obviously a major inconvenience for her. But, if it does,
best to know it early.

``Erin there are people out there who are attracted to things far outside the realm of what
is considered normal. Some are attracted to things that are bizarre.''

She had a troubled look on her face, and I was sure this was going to end badly, but I
pressed on. ``There is a fairly large group who are very excited by seeing a woman in a cast.''

Her eyes furrowed as she blurted out ``You mean there are perverts out there who get their
jollies from the pain I went through?!''

``No, I don't know of any who are turned on by the pain or suffering. The ones I know of are
simply excited by the cast.''

I was trying to calm her down, even if this whole thing turned out to be a wash. ``I have
heard several theories on the subject, some think that the perceived vulnerability is what does
it. Others think it is the extra care that a person challenged by an injury would need. For
some, it is simply a bondage issue. Some think it may be a combination of these, but nobody
claims that they like it because of the pain and suffering. Mainly, the audience I work for is
adamant that he does not enjoy the injury, only the cast. In fact, he feels a bit of guilt over
the fact that what turns him on is a byproduct of an injury to someone else. That's why he hired
me.''

She still looked upset, but maybe not as much as she was.

``And what exactly is it that you do for him?'' She asked.

``I am an artist and photographer,'' I replied. ``I provide him with photos and sketches of
beautiful women in casts. Since it is not everyday that you find a woman in a cast, I apply
casts to women, and they serve as models for my work.''

``This is weird. Too weird. So how did you come to this? What made you this way?''

For a moment, I considered telling her the truth. Her beauty and emotional strength were
extremely alluring to me. Maybe. Maybe it was just the cast. I decided to stick to the stock
story. I explained that I was just hired help, too. Hired by a wealthy man who wished to keep
his identity secret, for obvious reasons. He was the one who financed all of this, and while I
appreciated female beauty, the casts really did nothing for me.

``Strange way to make a living.'' She spouted.

``Yes, but better than having to try to do more mainstream art, and make a living doing the
same thing as thousands of other artists. And it sure beats holding down a nine to five job. In
addition, not only do I have this great house for a studio, but I get to live here rent free.''

``Good point,'' she said. ``It is a cool place.'' She seemed to be softening, but I wanted
to find out.

``Anyway, in case you might still have any interest, here is the proposal: I need two or
three models to work one or two days per week. On the day you work, you would start at 9:00 am.
You will be placed on a cast, or maybe more than one. After they set, I will photograph you, and
then do a sketch of you. After that, you will be cut out of your casts; (minus the one you came
in with, in your case) paid, and sent home by 5:00 p.m. Some days, I might want to start a bit
later, but I would let you know in advance. The pay is in cash, and we obviously want
discretion- we would prefer you don't tell anyone about this.

``This is unbelievable,'' She said. ``Here, I'd give anything to be rid of this cast, and
yet I'm being asked to wear more of them.''

``I know it seems really odd, but you don't have to decide now. Also, if you try it, and
find that you don't want to continue, you can stop at any time, even if it is in the middle of a
session. And, we do pay well.''

``How well?''

``We graduate the pay based on exactly how you are casted. The lowest pay we have is two
hundred dollars, which would be for a below the knee cast on your leg, or a below the elbow arm
cast. The highest paying cast would be six to seven hundred dollars, but to get there, we'd be
talking about a body cast, maybe with an arm or leg included. Maybe I can arrange for a bit
extra for the cast you'll be bringing with you.''

This is really freaky. I need to make some money, since I can't work with my leg like this,
but I just don't know. Can I think about it awhile and call you?''

I wanted to prod her to say yes, but knew that was a bad idea. ``Absolutely.'' I told her.
``I need two or three, maybe even four models, and I have one strong candidate already. I'm
offering the second spot to you. If you decide to take it, it's yours as long as it is still
open.'' There- not forceful but hopefully giving her a sense of urgency.

``Fair enough.'' She replied. I won't take too long to decide, and if the job is gone, then
I'll know it wasn't for me.'' She lifted her leg out of the stand, and lifted herself up with
her crutches. I showed her to the door, and watched her hobble down the walk on her crutches.

I went to the parlor and lit a cigarette. I really hoped she'd take the job. I really wanted
to cast her, and I wanted to do it more than once. I wasn't sure if it was her or her cast, but
I wanted to cast her more than any of the women I had casted already. I got up and went to
finish the painting in the new ``hospital room,'' still thinking about the woman I had just
interviewed.

The phone interrupted my work.

``Hello.''

``Hi Quinn, it's Monique.''

``Hi Monique. What's up?''

``I have something I need to talk to you about. Can I come over?''

``I guess so.''

``Great, I'll be there in half an hour.''
