\chapter{Dinner}
Sunday morning, I awoke feeling peculiar. It was that strange ``did I just dream that, or did
it really happen?'' feeling I get after a day where something odd happens. I shook the sleep out
of my head, and realized that the previous day had indeed happened as I remembered.

Dinner with Monique had been enjoyable to a point. Nothing fancy, we had burgers and beers
at a local pub.

The conversation was interesting, to say the least. We traded some very basic personal info.
I had to make most of mine up on the fly to conceal the facts about me, and hers was very
interesting: Some of it, I had already heard. She was born in Paris to a French father and
Vietnamese mother. She lived there until she was 8 years old, when they moved to Pittsburgh. Her
father died when she was 14, and she and her mother had a rough time of things ever since.

She came to this school studying education on a partial scholarship, but was working to pay
the rest of the expenses. The thought of her wanting to be a teacher was a surprise, since
teaching is not an occupation that would be the first choice of someone that was highly
materialistic.

Her conversation turned shortly to casts. She wanted to know more about the casts she had
just worn- what sort of injuries they treated. She also asked about casts that she had seen that
were in colors other than white, so I explained fiberglass vs. plaster to her. I even touched on
the strong and weak points of each. She asked if I ever used fiberglass, and I told her I did.

It was truly bizarre, being questioned in depth about casts and casting by a beautiful woman
who seemed quite interested in the whole concept. I reminded myself that this was a beautiful
woman who also had a cold and calculating side to her, with too much fondness for money, and
that's when it dawned on me- She didn't have any other interest in casts besides the money she
could make wearing them. Of course, had to be it! She really didn't care about casting, only the
money that it brought her. Hell, maybe she hoped to meet the ``man behind this,'' and get closer
to the money. Stupid me- for a short time, I was wondering if she really might like it. After
that, my answers became a little shorter, though not rude, and I was glad to take her home when
we were through.

Now, dressed and downstairs, I attack the mess from the day before. Two cutoff casts, in
Monique's well proportioned shape, and a lot of bandage wrappers and plaster drips. Still, it
was well worth it.

Monique woke up in a similar state of mind. She had to pause to recollect whether the
memories she had were dreams or reality. A quick feel into the pocket of her shorts was all she
needed. The money was there. Thankfully. Yes, she needed the cash; of that there was no doubt.
But she could no longer deny to herself that she did it only for the cash.

You liked it, and you know it. She thought to herself. You enjoyed the whole day, from the
casts, to the company. God only knows why- it is most certainly NOT right, but you did, just the
same. You enjoyed having those casts put on, you enjoyed them once they were set, you enjoyed
dinner afterwards, and you enjoyed who you did it with. But, did I really enjoy everything? Did
you really enjoy the casts, or did you just enjoy Quinn's company? Did you really enjoy Quinn's
company, or was it just that the casts made a profound impact on you that you naturally enjoy
him, since he introduced you to it?

Deciding that these questions were too much to think about, and that she didn't have an
answer anyway, she got showered and dressed. Still thinking about the previous night, she
decided to follow the impulses a bit longer, at least until she put them out of the front of her
mind.

Diane, her roommate who had first told her about Quinn, was still asleep upstairs, probably
not alone, either. Diane was emotionally weak, and never felt complete unless she was in some
sort of relationship, even if it was a bad one. Monique decided to take a few minutes to try
something on the computer.

She logged on to the Internet, pulled up a search engine, and entered ``plaster cast'' in the
search field. Most of the results were not of much interest, but one stuck out: ``Plaster of
paradise- resource page for those who want to wear casts'' her heart jumped a beat as she read
the words. She clicked the link, and was introduced into a world she would never have dreamed of
only a few weeks ago. She saw pictures, stories, anecdotes and other information, all by, and to
people who had an interest in wearing casts or seeing other people casted. She surfed the sites
for a couple of hours, until she was no longer the only one in then house awake. She excused
herself, and went out for a walk.

Walking in the warm morning air, her thoughts churned. She thought of some of the things she
had read and seen. She thought of some of the casts that looked interesting to her, and some of
the stories, both true and fictional, about wearing casts. Some of the casts looked like fun,
and some looked a bit too intense. She thought about how it would feel to wear some of those
casts, and the thoughts stirred heat within her. She definitely wanted to wear some of these
casts, and she wanted Quinn to be the one to put them on her. She thought of turning for home,
and calling Quinn and telling him the truth, and hoping he would (could) agree to cast her
again, maybe even today.

You really have lost it, haven't you? Just take down every defense you have, when you have
seen that this guy has his moody streaks. Sometimes he is warm and friendly, while other times
it almost seems like he can barely stand to be around you. Maybe that is part of the attraction
you have to him. He doesn't fawn all over himself because of the way you look.

Well, at least one thing is nice- you did finally admit that you ARE attracted to him. But
you can't call him again- not now, anyway. Maybe in a week or two, before summer session begins.
Unless you come to your senses and realize what a bad idea it is first. Maybe you should just
run from this. Better a little hurt now than a lot of hurt later.

Monique's feelings were torn down the middle as she walked aimlessly for the rest of the
morning, and part of the afternoon.
