\chapter{Unexpected Inspiration}
    After the session where I placed Angie in the long arm cast, I noticed a dent in my supply
of casting materials. While certainly not enough to shut me down, my nature is to keep plenty of
``necessities'' on hand, just to be prepared for any eventuality. I needed to make a supply run.

The college town where I currently live is too small to have any sort of medical supply house
that would be well-stocked, so I get my supplies from a city to the north. There is a medical
supply house there that has everything I need. They ship within a few days, but since this was a
beautiful Saturday morning, I decided to make a road trip. I started up the old Mustang, and
headed north.

At the supply house, I picked up some padding, plaster and fiberglass. While I was there, I
selected a pair of walking heels, and a pair of arm slings. I'm not sure when or if I will use
them, but they looked interesting, and I decided that I needed them in my inventory.

With the supplies loaded in the trunk, I stopped at the local library, where I perused the old
orthopedic textbooks. I couldn't help but be fascinated by some of the huge body casts I saw. Of
course, I read all of the cast-making techniques I could find. I've always liked the idea of
larger casts, and I'd like to put one on a model sometime soon.

On my way out of the library, I noticed a couple of teenage boys admiring my car.

``Nice car. Is it a real Shelby Mustang?'' one asked.

``Yes,'' I replied. ``Restored to original.''

``It sure looks great. Are you headed to the Dog Stand?''

``What is that?'' I asked.

``It's a little drive-in restaurant around the corner. Every Saturday night, they have a car
show there. Nothing fancy or organized, just people driving their nice cars in to show and talk
with people.''


A asked directions, and told him that I would be there. It might be fun, if there were more than
a few cars there.


The show turned out to be very impressive, considering there seemed to be no organization to it.
There were at least 100 old cars there, maybe as many as 150. There were quite a few people
there, as well. I parked the Mustang, and raised the hood, as this seemed to be what most others
had done. I talked with a small swarm of people who came up to the car as I parked, answering
questions, hearing about the car ``their uncle had like that one,'' and such. After the group
had moved on, I decided to walk around and see some of the other cars there. While walking
toward an old Thunderbird that has caught my eye, I saw something that stopped me dead in my
tracks.

I'd estimate that she was 25 years old, maybe as much as 30. She had long brown hair, and a
beautifully proportioned figure. She had a gorgeous face with narrow elongated features, and she
had obviously been in some sort of terrible accident.

She moved along fairly well, but her steps were obviously taken very gingerly. Her left arm was
in a long arm cast. I could see that the light blue fiberglass disappeared under her T-shirt
sleeve. Her right arm was in a matching short arm cast. What totally floored me, though, was her
other piece of ``hardware.'' She wore a large back brace over her T-shirt. I couldn't remember
the name of it offhand, but I knew that I had seen one before on the internet. (later that
night, I would find out that it was a CTLSO.) At that moment, however, I was simply fascinated
with watching her move around in the plastic and steel contraption. She was holding the arm of
what must have been her boyfriend or husband with her right arm for support. I followed them
from a distance, watching them enjoy the show. I mentally kicked myself for having left my
camera at home. I noticed several other people looking up to enjoy her ``show'' as well. You had
to admire the fact that she was out having a good time, even though she was injured and
obviously had some trouble in ambulating.

After a while, the woman and her escort left the show. I knew that the show had nothing more for
me, having just had that remarkable sighting, so I left as well. During the 50 mile drive back
to my studio, I thought over what I had seen at the show, and what I had seen in the library
books, and decided that my plans for my next project had just changed.

The next day, I called April, who I was scheduled to cast photograph and sketch Tuesday evening.
I told her that I wanted to change the original plan for the cast she would wear, and told her
what I had decided. She agreed.
