\chapter{}
Detective Cassidy Smith sat at her desk, looking over a report one last time before she
turned it in. She hated paperwork, but she loved being a cop. She'd wanted to be a Police
officer since she was a little girl. She'd done well in school, and her parents had cringed when
she had told them her college major was going to be Criminology, with a Psychology minor.

After graduation, she'd come to this town, and had made Detective after only two years. Now,
at age 26, she had more decorations and commendations than most officers at retirement's door.
She also had the respect of the officers she worked with, despite her gender, age and looks.

Detective Johnson walked in. ``Hi, Cass. How's it going?''

``Fine. What's up?''

Cassidy liked working with Tom Johnson. He was smart, and tough- the kind of guy you wanted
with you in a tight spot. Last year, they'd worked together to catch a lowlife who'd been
abducting, raping and beating young women. Cassidy had been the bait, and when the scumbag had
gone for her, Johnson had closed in so fast; the guy never knew what had hit him. Johnson was
also very dedicated to his family: an all- around admirable guy.

``What's the project, Tom?''

``Young women see ads for models in newspaper. They call, they go, guy seems nice, share a
soda or beer, take some pictures, next thing they know, they're waking up, having slept with the
guy, but not remembering it.

``Drugged.''

``Yep- Ketamine Hydrochloride in every case.''

``Good old Special K- it never gets old,'' she said.

``Here's the kicker- look at the locations: Small college town near Detroit, small college
town near Chicago, small college town near Indianapolis. Do you see a pattern, here?''

``Yeah,'' she said. ``It looks like he's moving. Our way, no less.''

``He likes college girls, and we're right in the path of destruction,'' Johnson said.

``So, let me guess,'' Cassidy said. ``I'm going back to school?''

Johnson smiled. ``No better way to catch a fly than with sugar.''

``Oh, my- I believe I've just been a victim of sexual harassment, Cass said, joking.

``Yeah, sure, and if I'd really harassed you, I'd probably be spitting out teeth right
now.''

``Violence?'' Cassidy asked, batting her eyes. ``From sugar such as I?''

``Yeah- whatever. Anyway, take a look at this. He tossed down a copy of Kicks, opened to the
ad section. Cassidy read aloud the ad that Johnson had circled:

``Models wanted no experience necessary. Week's pay for a day's work. No nudity, but an open
mind is required.'' She handed it back to Johnson. ``We need to call the paper and see what they
can tell us about the person who bought this ad.

Johnson was ready. ``The guy's name is Quinn, he doesn't show priors in any database, and
doesn't have a driver's license in this state. They're still checking on other states. The paper
also said that this is the first week that the ad has run.''

``Then I guess it's time to give this Quinn a call, and see just what he wants with
inexperienced models,'' Cass replied.

``Go ahead and call. We've already established the same cover at the college that we used
last year.''

``Pretty bold of you, doing that before you even asked me if I wanted in,'' she said,
turning to her desk, opening a drawer in search of a file.

``I know you Cass- you live for this kind of stuff. Going under to catch a dirtbag is fun to
you. I knew you'd want in, and I knew you would probably want to start right away.''

``Yeah, yeah- you're lucky you have me, all I have is you.'' She found the file she was
looking for- it had the details of fictitious college junior Samantha Cassidy: Age 21, Drama
major, and Psych minor. Class schedule, as well as other minor details that Cassidy would have
to learn again.

``Whatever, 'Sam.' Just make the call.''

``Yes sir!'' she said with a salute as she punched the button on her phone for the secure
line.
