\chapter{A Way Out}
Monique closed her textbook and sighed. She simply could not concentrate on global economics
tonight.

``This is college, I'm supposed to be having fun, not stressing myself to death,'' she muttered
to the empty apartment.

Monique was working her way through college, and not having an easy time at it. She was spending
so much time at her waitress job that her grades were starting to slip. On top of that, tips had
been sparse lately, and what once had been barely enough to see her through was just not enough
lately.

``Maybe I should just enroll at school back home,'' she added.

Of course, to do that would be to admit failure. She had told all of her family and friends that
she would make it, despite their protests. Now, there just wasn't enough money for books,
tuition and living expenses.

Her mother couldn't help: she was barely getting by as well. Her father had been an artist of
moderate success, and had moved the family to the United States when Monique was ten years old.
Five years later, when he died, he left Monique's mother with very little, and that had
evaporated quickly. Her mother worked long hours at menial jobs to keep food on the table and a
roof over their heads. Monique remembered the confident way she had told her mother that she was
going to go to college, and pay for it, herself.

As she was scolding herself for her pride and overconfidence, the front door swung open, and in
walked her roommate.

``Hey, Monique- what's going on?''

``Hello, Diane.''

Diane noticed the despair in Monique's voice

``What's wrong?''

``I can't concentrate worth a damn. Midterm is next week, and if I don't do well, I'm really
going to be in a hole with this class. Not that it's going to mean much in the long run, I'm not
even sure if I'm going to be able to come up with my part of the rent this month.''

``Come with me,'' Diane said. ``You're obviously in dire need of a beer or two. Besides, I have
an idea that just might ease your money crunch.''

``What would that be? A winning lottery ticket, or a rich, single doctor?''

``Neither. Just a job. Probably the strangest job you could ever have, but probably the easiest
and best paying one, too.''

``Now, I'm really wondering what sort of insanity you have in mind. What is it?''

``I'll tell you over a drink- my treat,'' Diane said.

At the pub, they each ordered a beer and sat at a corner table. Diane took a folded piece of
newspaper from her purse, opened it, then handed it to Monique. Monique looked at the classified
ad that had been circled. The heading was ``Models wanted, no experience necessary.''

After she had read the ad, Monique looked up to see that Diane had laid four one hundred dollar
bills side by side on the table in front of herself.

``You're looking at five hours work there,'' Diane said. ``Most of which was spent sitting on my
butt.''

``OK, what's the catch?''

``This guy is an artist. He does photography and sketches of women wearing casts.''

``WHAT?!?!?''

``That's right, casts. Just like one you would wear if you had broken a bone.''

``Before I ask why, can I ask why you? You're not wearing a cast.''

``No, I'm not,'' Diane replied ``But I was last week. He put a cast on my leg, took his
pictures, made his sketch,then took the cast off. He paid me, thanked me, and asked if I knew of
anyone else that might be interested in posing for him.''

Monique was truly puzzled, now.

``Why does he do this? Is it for some book or magazine?''

``That's the strangest part of it. He says that he does this for a rich patron. Supposedly, this
rich guy set him up with a studio, and foots the bill for all of this. I think the guy must get
off on it.''

``Alright, Di. You're kidding me, aren't you?''

``Monique, I swear this is true. As pinched as you are for cash right now, I'd never joke about
money.''

Monique finished her beer, then said: ``This is more than a little bit creepy, a rich guy who
gets turned on by women in casts?''

``It shocked the hell out of me, too. I almost got up and left when Quinn told me what he
wanted. The only reason I didn't was because he seemed like such a nice guy.''

``Quinn? Who is that? The rich freak?''

Diane asked the waitress for another round, then continued:

``No, Quinn is the artist. I never met the man who finances this.''

In her mind, Monique started to ponder this opportunity. It certainly was high on the
weird-o-meter, but four hundred dollars would give her some much needed breathing room in her
finances.

``So, what was this so-called artist like? You said his name was Quinn.''

``He was very nice. When he was putting the cast on my leg, he made sure that he didn't touch me
in any sexual way. I could tell he was being careful. And considering how high on my leg the
cast went, it wasn't easy. He might be gay, but it would be a shame-he's cute!''

``What about the cast? How did he make it? How did he take it off?''

``He did it just like a doctor would. Have you ever had a cast?''

``No''

``I had one when I broke my leg, and I remember how the doctor did my cast.'' Diane went on to
explain to Monique how the cast was made, and how it was removed. She made sure to tell her
about the removal saw, and how it would not cut skin.

``Alright, Diane--as broke as I am, I'll think about this. Do you think he would want to work
with me?''

``Monique- you are gorgeous. Between the way you look, and that little accent of yours, he's
bound to be charmed.''

``Alright, alright- I'll give him a call tomorrow.''

Diane handed Monique her cell phone.

``Call him now, while you still have your 'beer bravado.'''

Monique took the phone, and dialed the number in the ad.
