\chapter{Models Wanted}

``Models Wanted -- No Experience Necessary -- Local ladies needed to sit for artist. No nudity,
but an open mind is required! Top pay.''

I remember the day it all started. I pondered the classified ad for a while before I sent it
to Kicks. Kicks is a local newspaper, catering to the 18-25 year old crowd. It got started by
some enthusiastic journalism students at the college. After its first year, it became extremely
popular. So popular that it was able to sell advertising space so easily that it could actually
circulate for free. After these students graduated, they kept it going, as it became quite
lucrative for them, despite the fact that it is distributed for free. Almost every college
student has their set place where they pick up their copy every week.

The paper has quite a personals/classified ad section, where one can usually find anything
from someone selling a mountain bike to lesbian biker women looking for a third.

It hadn't been long since I'd settled near town before I got my idea. I've always loved the
idea of casting women, and sketching or painting them afterwards.

Oh, I've had girlfriends in the past who would have been more than willing to participate in
almost anything I asked them to. I've had a lifetime of ``yes-men'' and ``yes-women'' who did
everything they could to make me happy. Of course, they were only doing it because my family was
wealthy. They would gladly have participated in my art, not for the sake of my art, but for the
sake of my money. While most of the time, I would have preferred to have been alone, I put up
with these people to keep my father happy. He worked so hard to make us rich, he wanted us to
experience every benefit that money could bring. I played along, mostly out of respect for him.
I even got to go to a great school to pursue my art studies. The only casting I ever got to do
was on myself, hoping for the day when I could cast a beautiful woman.

After the death of my parents, I decided to change things around a bit. I sold all the
houses except the one in Florida, (That was my dad's favorite house) and all of the other
trappings that come with money. I invested the money, and took off in an old muscle car (OK, so
I kept one indulgence) to see America. I roamed around the country for a few years, sometimes
staying in a place for a few months, sometimes, just passing through. There is a whole other
America out on the country roads, and I loved experiencing it.

I came to this town about a month ago. One day, I saw two coeds going to class. One of them
was on crutches, with a pink long leg cast. She was very pretty, and I couldn't help but sneak a
good stare at her, crutching along, chatting with her friend. At that point, inspiration hit the
way it always does- Suddenly, completely, and without warning. I knew what I wanted to do.

I found an old Victorian style house in town that was for rent. It was perfect- it would be
a nice place to live, and an excellent studio. I went around the antique malls and bought some
very nice furniture for the downstairs. It would be the perfect backdrop for photos and drawings
of casted women.

I chose one of the downstairs rooms to serve as the casting area. A couple of quick phone
calls netted me all of the items I could imagine I might need. I acquired a medical exam table,
a few sets of crutches, to accommodate differing heights, and a wheelchair. I made sure that the
wheelchair had a reclining back, just in case I decided to do a hip spica, and had to move a
woman so casted.

I also found a medical supply house that would sell casting supplies to me. I was a bit
nervous about asking, but apparently they were more interested in making the sale than the
reason for my buying. I purchased padding, stockinette, and plaster, all in varying widths. I
also bought quite a supply of fiberglass bandages, in varying widths and colors. I didn't want
to have to plan ahead on anything. I wanted to be ready for any sort of cast that I decided to
do. I took the supplies to the casting area, and stocked up my cart that I had bought to work
from.

My last step was to call the paper about placing the ad. I got the prices and deadline
schedule. I thought for a while about the wording, then wrote it out, and dropped it in the
mail.

With the ad in the mail, the wheels were in motion. That left me only to wait for the first
call.
