\chapter{Tanya}
As Spring rolled into Summer, my phone didn't ring nearly as much. No doubt, this was caused
by the fact that most students went home for the summer, or were off doing other things, once
the spring semester finished.

With plenty of time on my hands, I decided to get away for awhile, so I got on a plane and
headed for the Bahamas. The trip was wonderful- sun and sand are always good for the soul.

While in Nassau, I had a very pleasant cast encounter. I was walking along the beach when I
saw her. She was tall and blonde, with very pleasant looking facial features. She wore her hair
pulled back into a pony tail, and covered with a baseball cap. She wore an oversized printed
white T-shirt, canvas shorts, and a flip-flop sandal on her left foot. Her left foot, however,
is not what you want to hear about, is it?

Her right leg was covered in blue fiberglass. It started at her toes and went all the way up
until it disappeared under the khaki colored shorts.

The fiberglass was a darker blue than any I'd seen before- it was actually a navy blue, and
I liked the color instantly.

She had a small gym bag in one hand, and carried aluminum crutches under the other as she
hobbled out nearer to the water. I noticed she had a plastic bag over the toes of her casted
foot, and that it was secured with a rubber band. Good idea- I can imagine that sand in a cast
would not be very comfortable!

I followed her with my eyes until she had gotten to a point on the beach that she liked. She
dropped the crutches, and opened the gym bag. She pulled a large beach towel from it, and spread
it out on the white sand. She then proceeded to unfasten her shorts and let them fall to the
ground. She quickly hopped her left foot out, then carefully, with as much grace as possible,
lowered herself to the ground. Once down, she leaned forward, and slipped the shorts off of her
casted foot. She then removed the T-shirt, revealing the black bikini she wore underneath.

It was obvious that sunbathing was a normal pastime for her, as she had a very beautiful,
natural looking tan. She finished preparing by removing the plastic bag from her right toes,
revealing that the toenails were painted to match the cast- cute touch.

I kicked myself for not having my camera with me- what a great candid photo this would have
made! I decided to go back to my room to get the camera. With all of the trouble she went
through to get to that beach, she probably was not going to leave anytime soon.

Back at my hotel room, I glanced at my cell phone to see if the indicator showed any voice
mail. It did, so I called to retrieve my message.

``Hello, my name is Tanya, and I'm calling in regard to your ad for models. Please call me
back,'' and she left her number. Since my sighting had me in ‘full casting mode,'' I decided to
call her back immediately.

``Hello,'' said the pleasant female voice.

``May I speak to Tanya?''

``This is Tanya,'' returned the pleasant voice.

``Hi, I'm returning your call about the modeling job.''

``I'm curious as to what sort of modeling it is.'' The on the spot question. I thought of the
casted woman on the beach. I didn't want to lose the photo opportunity, so I didn't hedge around
the subject.

``Tanya, for this job, you will be placed on one or more medical style casts. Afterwards, I
will take photos of you in your cast, then make a sketch of you.'' There, that was a quick
enough
way to say it. The phone line was silent for a few moments, followed by her saying ``What?''

``It's true,'' I said, launching into my canned cover story about the moneyed patron and my
assignment.

Another pause, then she said ``That's really bizarre. How much does it pay? How long does it
take?''

``It usually takes three to five hours, depending of the type and number of casts, and the
pay varies, as well. The more you are casted, the more money you are paid. The absolute minimum
is three hundred dollars.''

``That's not bad money for a half day's work. So, would I be nude except for the casts?''

``No, absolutely not,'' I replied. ``We like for you to wear either lingerie or a bathing suit
for the sessions.''

``Wow, that really is bizarre,'' she said ``but I could use the money. How soon could we do
it?''

``Tanya, I can't commit to doing it until I see you in person. The man paying for this likes
certain types of women, and I'd have to be sure you fit in.''

``I see. When can we meet?'' she asked. She must have been in need of quick cash.

``Let's do this- We'll meet Friday at 2:00 p.m. Bring along a bathing suit or lingerie. That
way, assuming you're the type we're looking for, we can go ahead and do it then, OK?''

``That sounds great. Where do I need to be?'' I gave her the address, and told her I was
looking forward to meeting her.

After I hung up, my casting excitement was at full stir. I began packing so I could get home
and get ready. I was halfway through my call to the airline when I remembered the woman in the
LLC on the beach.

``Shit!'' I said. I finished the reservation call, grabbed my camera, and rushed back out to
the beach- my subject, however was gone. I kicked myself for not having the camera with me in
the first place. Still, it was a very nice sighting, and I'd never seen fiberglass in that dark
of a blue before. I made a mental note to find some of that color as I headed back to the hotel.
The stranger on the beach, destined for some very odd tan lines, remained on my mind all the way
home.

Thursday was very busy- After gathering up the pile of newspapers, and dusting, I made a
trip to renew my supply of plaster. The long leg cast and long arm thumb spica that I had made
on Monique had dwindled my supply. Yuck, why did I have to go and think about HER? Lousy
gold-digger.

``Because,'' I answered myself aloud, ``gold digger or not, she looked fantastic in those
casts!'' Whatever. It was a shame that all that beauty was wasted on a woman with so little
substance.

After I returned from the supply run, I relaxed on the front porch with a Diet Coke and a
cigarette, while my mind played out different casting scenarios possible for Tanya.

Friday, at ten minutes past two, the doorbell rang. I opened the door to a woman of
remarkable beauty. She had long permed brown hair, brown eyes, and very pleasant facial
features. As I let my eyes drift down, I quickly realized that she definitely ``fit in'' as a
model.

``Tanya?''

``Yes. You must be Quinn. I'm sorry I'm late, but I got lost.'' She said with a smile.

``That's not a problem. Come in,'' I said, leading her to the parlor, and motioning for her to
sit. I offered her a soda, and by the time I had returned, I knew how I wanted to cast her, as
long as she was willing.

``Tanya,'' I said as I sat down, ``what I would like to do is to put you in a shoulder spica
cast.''

``I guess that means I qualify.'' She said with a sly smile.

``Definitely. You're more than qualified.'' I smiled back.

``So, what is this shoulder spica cast?''

``A shoulder spica cast starts at your waist, covers your torso, one shoulder, and that
entire arm as well. Medically, it is used to immobilize fractures of the upper arm bone. It is a
big, heavy cast, and I'll pay you \$450.00 for modeling it.''

``Wow. Very good money. How do you get me out of it once we're through?''

``The exact same way that a doctor would. Come with me and I'll show you.''

I led her into the casting room, and retrieved the cast saw from its place in the cabinet. I
plugged the saw in, turned it on, and held the oscillating blade against my left hand.

``This instrument is a medical cast saw. ``I began. ``the blade moves back and forth instead of
rotating. What this means is that it will cut hard objects very well, but with something soft,
like skin, it simply vibrates. It's totally safe- there's no way it can cut you.''

``Well,'' she said ``I've never worn a cast before, so I might as well start big. ``I'm ready
whenever you are.''

``Alright, I'll leave you to get ready. What did you bring to wear?''

``I brought a swimsuit along. It's a one-piece. I also, of course, have my underwear on
beneath my clothes.''

``Let's just go with the underwear,'' I said. ``Considering the type of cast we're going to be
making on you, a one piece swimsuit could cause major troubles if you need to use the
restroom.''

``Yes, I suppose that could be a very bad thing,'' she said with a slight smile.

I left her and quickly went to the garage. I got an old hacksaw and a broom handle that I
had kept around for this occasion. On my way back, I stopped in the kitchen for an envelope. I
placed the bills inside, and returned to the casting room. Tanya's eyes got huge when she saw
the hacksaw.

``This is just to cut the brace that helps hold your arm out,'' I reassured her.

Standing there, in nothing but her white underwear, she looked amazing. She was going to
make an excellent model for this cast! I asked her to slide her bra strap under her arm on the
right side, as that shoulder would remain bare. When she had done this, I handed her the
envelope and said: ``If you're ready, we'll begin.'' She looked in the envelope, nodded her
head,
and I began working.

I took my roll of twelve inch stockinette, and cut off four feet of it. I had her hold her
arms straight up while I slid it down over her body, past her hips. I then made slits down each
side from the top to where the stockinette rested under her armpits, and allowed her to lower
her arms. I pulled the front and back halves of the stockinette together over her left shoulder
and taped them into place. I then took a roll of three inch stockinette, and slid this onto her
left arm all the way to her shoulder. I trimmed this off at her fingertips, and made a slit for
her thumb to pass through. As I was doing this, I was explaining the process to her: ``This is
stockinette, which keeps the padding from irritating your skin. Next comes the padding, which
will make this cast much more comfortable to wear. What I need for you to do is to hold your arm
out at your side like this.'' I took her arm, and held it so that her upper arm was at a 90
degree angle to her body, and the elbow at a 90 degree angle. I then handed her the broom handle
to hold onto to steady her arm and keep her muscles from fatiguing.

I took a roll of 6 inch padding, and began wrapping her body at the hips. I worked my way up
over her waist and torso, keeping the padding slightly taut so that it would conform to her
curves without bunching. As I got to her chest, I loosened my wrapping just a bit, however. I
then took a roll of four inch padding, and began wrapping her upper arm, working over the
shoulder. I made a couple of passes between her breasts in a figure-eight style so that there
would be some separation. I took another roll of six inch padding, and used it to cover her
lower torso again, paying particular attention to her hip bones, since they bear a lot of the
weight of a shoulder spica. One more roll of four inch finished the upper torso and shoulder,
and two rolls of three inch took care of the rest of the arm and hand.

With her all padded and ready, I quickly measured the distance from her forearm to her hip
bone,, and took the broom handle from her just long enough to cut a piece to length. I gave it
back to her, and we were ready.

Nothing looks better for a shoulder spica than plaster, but I was afraid that it would take
forever to dry. I had decided to get a bit clever, though.

``Tanya, this type of cast looks much better in plaster. However, plaster takes a long time
to dry, and it would be very tiring on you having to wait. What I am going to do is to first
make the cast in fiberglass, then cover the fiberglass with a layer of plaster. In the end, it
will look every bit as good, but the process will be much easier for you this way.''

``If you say it's better this way, I appreciate your doing it like this.'' She replied.

I excused myself long enough to get the water. I filled the bucket with water at about room
temperature for the fiberglass. When I returned, I found her poking at the padding a bit with
her free hand.

``Checking it out?'' I asked.

``I was just seeing what it felt like on the outside,'' she replied. ``This is new to me, and
I'm just curious, that's all.''

``That's no problem. If you're ready, here's where it really gets interesting.'' I took out
several foil packets, and laid them on the table next to her.

``These are the fiberglass bandages. I will first dip them in the water, then start wrapping
them on you. As they begin to set, which will only be a few minutes, you will feel them getting
warm. The heat shouldn't be too uncomfortable, but if it gets that way, be sure to tell me.''

``OK''

I opened the first roll of four inch white fiberglass, dipped it, and began wrapping her
upper arm. I worked my way over her shoulder, and chest, being careful not to smash her breasts
under the bandage. I began where I did so that this area would begin to set up first. The next
roll was five inch, and I used it to continue the cast down to her hips. I then took another
roll of five inch, and laid it directly over the last one. I then took two more rolls of four
inch, and wrapped them over her chest, shoulder and upper arm, to strengthen this area. Once
this was done, I used three more rolls of four inch to cover her arm down to the wrist, and a
roll of three inch for her hand. I finished the fiberglass work with one final roll of five inch
from her hips to her chest. I could see the water sweating out of the fiberglass in places, and
I felt the heat from the exothermic reaction of the fiber.

``We're all done with that part, Tanya- how is the heat?''

``It's not bad. I can feel it, but it's not uncomfortable, though.''

``Good. In a few minutes, you won't need the broom handle anymore. That fiberglass gets solid
fast.''

``It's almost kind of $\ldots$ Cozy,'' she said.'' Can I relax my arm, yet- It's starting to get
tired.''

``Not just yet, but soon- it's got to sound good by now, though.''

``Actually,'' she confessed ''I'm mostly relaxed already. I hope that doesn't screw things
up.''

``For what we're doing, probably not. Just don't try to strain against it.''

``OK''

I excused myself again to change the water in the bucket. This time I got water as hot as I
could stand. With an entire cast already on, the heat wouldn't bother her, and it would make the
plaster set quicker. When I returned, I asked if she was ready to continue. She nodded.

I began by trimming the padding back to the edges of the cast, and then trimmed the
stockinette, leaving it long enough to anchor. Now, for the plaster!

I began with a roll of five inch plaster, and began at her hips. I worked upwards, using two
layers of plaster over the fiberglass. I found two layers to be enough to make the cast look
like it were constructed solely out of plaster. Five more rolls of plaster in varying widths
covered the fiberglass very nicely. When that was done, I took another roll of four inch, held
the broom handle in place, and carefully plastered it to her waist. This was tricky, and another
pair of hands would have been nice, but I managed. One more roll of three inch plaster anchored
the broom handle to her forearm, and covered the wood. I'm sure that it wasn't as strong as it
would need to be for a full plaster shoulder spica, but, like the plaster, the bar was only for
show anyway.

It only took about ten minutes for the plaster to get pretty well set. It was still damp,
and giving off a lot of heat, but it was Ok for her to move around, by this point, the
fiberglass was pretty well as hard as it was going to get. I asked if she needed anything before
we moved on the photos and sketching. She said she could use a trip to the restroom, so I led
her there, told her to be careful, and waited outside in case she needed any help. As she came
out, she said: ``Wow, this thing weighs a ton!''

``Is it comfortable,'' I asked. ``can you breathe easily?''

``It's not uncomfortable. It's odd, but it's kind of cozy. It's very strange not being able
to move my arm at all. It almost seems as though it's not even a part of me. It just moves with
my body.''

``Actually, that's a fairly common reaction from someone wearing their first cast,'' I
replied. ``Are you ready to finish?''

``Yes.''

I led her to the back bedroom, and had her sit in the chair by the window. The outside made
a nice backdrop- it gave a sense of connection with the outside world. I remember thinking to
myself how fantastic it would be to take a beautiful woman outside, casted like this. Not only
outside, but out in public- it would be great to watch the reactions of the people we
encountered. Of course, it was impossible- this was a small college town. Even if a model were
that brave, she would either have to wear the cast for a full term, or explain why she had the
cast for only one day. I'd rather not have too many people know what I was doing, as I'm sure
there would be a negative backlash.

I took several photos of her, then I decided to have her stand by the bed for the sketch.
This would be a very sensual pose. She stood next to the bed, and even placed one knee on it, so
she was halfway on it. Tanya was so beautiful that this would have been a very sexy pose without
the cast. With the cast, however, it was almost too much! I quickly worked through the sketch,
and it turned out very nicely. When I was done, I showed it to her. She nodded her approval and
said: ``Can I get out of this cast yet?''

``Absolutely- lets go cut you free.''

``Thanks, it's starting to get me a bit claustrophobic.''

I led her back to the casting room, which was a mess, to say the least. I took my saw, and
made three cuts, working as quickly as I could. One cut started at her right armpit, and
continued to her waist. The second started at her neck, and continued down the top of her arm to
the fingers. The final cut ran the length of her arm along the bottom, then down the side of her
torso to where the cast ended at her hip. Two quick cuts of the padding and stockinette on her
left side, the cast opened like a book, and out she came.

She pulled her bra strap back over her left shoulder and got dressed. She took her envelope,
we thanked each other, and she left. I began to clean up the trashed casting room. I took her
cast downstairs to add to my ``collection,'' and returned upstairs to my mess. As I was
cleaning,
the phone rang.

``Hello.''

``Quinn?''

``Yes. Who is this?''

``Quinn, this is Monique- do you remember me?''

Oh no!
