\chapter{}
Monique was right on time.

I greeted her at the door, and showed her inside. She was looking great as usual. She wore
jeans, a tight fitting tank top, and dark brown sandals. Though I had seen her feet more than
once, I couldn't help noticing that her toenails were painted, which was something new. I
suppose it was due to the fact that summer was almost upon us, and she was wearing open toes.
She pulled out the latest issue of Kicks from under her arm. It was folded open to the ad
section. She pointed to the new ad that I had placed.

``So, would experience help in getting this position?'' She asked with a smile. She really
did have a great smile.

Thinking of the new directions I wanted to go with the casting, I told her ``Sure, but a few
things will be different.''

``Oh? Like what?''

I decided to be bold. I wanted to try new things, and who better to pitch the idea to than
Monique? If she accepted, fine- she would make a nice guinea pig for future women. If she
didn't, it wasn't a terribly huge loss. Sure, she looked great in casts, but I still couldn't
get over my first impression of her as a moneygrubber.

``Well, Monique, the man who started this is happy with what I've done so far. He's happy
with your part in it, too. However, he told me the other day that he's not totally satisfied,
either.''

``I don't understand,'' she said.

``He wants things taken to a new level,'' I told her. ``A little more daring.''

Monique's heart sank at this. \aside{Oh no, he wants nude stuff.} She thought to herself.
\aside{I just can't do that. I'm really starting to like this- I'm not sure if I like Quinn, or
the casts, or both. But I am sure that I can't do pornography. It's just too degrading.}

``Daring how?'' She asked, sounding tentative.

``Well, for one thing, he really liked the bigger casts. He liked the body casts quite a
bit. He also liked it a lot when there was more than one cast. He wants to see more casts, and
bigger casts.

Monique felt her tension release. ``Well, I've worn two casts both times.'' She said. ``And
I wore a body cast the second time. I really didn't mind it.''

``True,'' I replied. ``But there's more. He really liked the outdoor photos. He told me he
definitely wants more outdoor photos. He also wants the indoor photos to have more medical
related equipment involved sometimes- crutches, wheelchair, even a hospital bed.''

It was all Monique could do to maintain her composure. ``So you're going to set up a
hospital room in here?''

``Actually, I'm almost finished with it.'' Are you interested in seeing it?''

``Sure.'' She hoped she didn't sound too enthusiastic.

I took her into the bedroom that I had converted. I showed her the bed and the various
attachments. I couldn't help but notice that her eyes got wide when she saw it. She was probably
a bit scared by it.

Monique looked at the ersatz hospital room- she couldn't believe it! The bed had a lot of
attachments – she wasn't sure what they were or how they worked, but she knew they were for
traction of various types. What she DID recognize were the two slings attached to the bed
already. She had seen enough pictures on the Internet to know those were for suspending casted
legs. She almost thought of asking if she could try those out right now.
``Wow, some setup,'' She said, regaining her composure.

``Yes, and there's one more thing that he wants to change too.''

``What's that?'' \aside{Oh no, please don't say nudity.}

``He'd like to see pictures and sketches done in public. Obviously, that would be tricky. It
would require traveling to nearby cities, to lessen the chance of running into someone either
one of us knows. It's escalation, to be sure, but the money will escalate, too.''

\begin{thought}
Wow, public. A chance to not only be vulnerable, but to see the reactions of people. She had
read on the Internet how many casters like to go out in public, mostly to see the reactions of
strangers. The daring aspect was intriguing, too. Yeah, I definitely want to do this!
\end{thought}

``How often would we cast?'' I found it surprising that she hadn't seized upon my money
comment and asked about that.

``Once a week.''

``Well, if you want me, count me in.'' she said, with no hesitation.

``Really? Even if it entails being out in public in casts, maybe even a body cast? It would
also mean you'd be casted for longer periods of time.''

``I don't mind, when do we start?''

``Don't you want to know about the increase in the money?''

``Sure, but I thought the money for this was pretty good before. If it's more now, I'm sure
it will be fine.''

That comment surprised me. Not what I would have expected from her, considering my
impressions of her. I detailed my plan to her about paying per cast, and the different prices
for each. I was going to have to write this down, so I didn't forget it.

``Sounds good. When do you want to start? Assuming, of course, the position is open to me.''

``Well, I assume you have finals about now. We should probably wait until those are over. I
don't want to cause you trouble with your classes.''

``Actually, I took my last final yesterday, so I am ready right now.'' She announced.

``Well, I wasn't prepared to start today.''

``Oh, I understand.'' She replied. ``I just wanted to let you know that I am ready whenever
you are.''

``You're sure you don't mind this? It will be more intense than where we've been before.
Maybe you'd like to think about it before accepting.''

``I'm sure,'' she said with confidence. ``It should be fun.''

Whoa, I didn't expect that remark either. Sometimes, I wondered if I was wrong about her.
No, probably not. This type of woman usually has an angle, and they're usually pretty smart
about getting what they want. Besides, my first impressions of people are almost never wrong.
