\chapter{~}
Friday morning arrived, and Monique was due any minute. I had phoned her Wednesday night to
tell her about the plans, and to give her instructions. The day promised to be very interesting.

I heard a car pull up outside, and I went to the window. I saw Monique get out of an older
Firebird. She was wearing shorts, just I had asked. My mind was going in several directions: I
was excited about the day's plans, but also a bit nervous. I was also feeling mixed emotions
about Monique: She really looked fantastic in denim shorts and a navy blue tank top, but her
attitude was something that I could never get far away from in my mind when I was around her.

As she walked to the door, Monique was also tentatively anxious about the day. \aside{``This
should
be great- a chance to be out in public, around a lot of people, while in a cast,} she thought to
herself. At the same time, the other side of her mind wondered \aside{``What if someone knows
I'm not
really hurt? What if someone asks questions? But then again, why WOULD anyone? You worry too
much! This is something you've been thinking about for a few weeks, and now you're going to get
to try it. Enjoy it, let it happen, and see if it's as fun as you think it will be.}

When she knocked at the door, I let her in. ``Good morning, Monique. Are you ready for
this?''

``Yes, it should be quite an experience.''

``You drove yourself this time. Did you get yourself a car?'' I asked.

``Actually, I've had it for a while, but it wasn't running. I just got it back from the shop
last week.'' She answered.

``Well, let's get started.'' I asked her ``Have you ever used crutches before?''

``Actually, I haven't. I've sprained my ankle a few times, but never anything I couldn't
walk on, she said''

I walked to the closet, and pulled out a pair of aluminum crutches. ``Let me guess- you're
about five feet, six inches tall?''

``Close,'' She said. ``Five, five.''

I adjusted the crutches to the correctly marked position. I handed them to her, and she put
them under her arms. I checked to make sure the height was right- almost, but not quite to the
armpits.

``I think they're a bit short,'' Monique said.

``Actually, they're just right. If you actually put your weight on your armpits, they will
get painful very quickly. Try taking a few steps with one leg off the ground.''

She bent her knee, and took a few steps with her left foot curled up behind her. She was
obviously new to it, but did pretty well.

\aside{``This is pretty easy.''} Monique thought to herself. \aside{``I might want to get a pair
of these for myself.''}

She crutched around the living room, then into the parlor and back.

``I think you're ready to use them for the day.'' I said. ``Let's get you into the cast, so
we can get going.''

``OK,'' she said, crutching to the casting room.

In the casting room, she hopped up onto the table, and pulled off her sandals. I told her to
take off her shorts so that we wouldn't get anything on them during the casting process. I went
to get her payment and fill the bucket with warm water.

When I returned, she was sitting thereon then table, legs hanging over the side. ``Damn,
black underwear,'' I thought to myself. There was something about black lingerie- it always had
an effect on me. I picked up the box of red fiberglass from the cart, and walked to the closet.

``Since you're all in blue already, let's try using the blue instead.'' I said. I grabbed a
box of four inch blue fiberglass, and set it on the cart, and took the rolls out.

``So we're going to use fiberglass this time?'' She asked.

I realized I hadn't told her about the fiberglass, but didn't think it was something that
would matter to her, as a model.

``Yes,'' I said. ``It dries faster than plaster. We'll be able to leave sooner by using it.
It goes on and comes off the same way, though.''

\aside{I finally get to wear fiberglass,} thought Monique. \aside{I've wanted to try this to see
what it was like. Most people on the internet seem to prefer one or the other.} Monique wasn't
sure if she had a preference. She liked the smoothness and ``classic'' look of the plaster, but
it wasn't used much in reality anymore, and she liked the colors of the fiberglass. \aside{Maybe
I'll have a preference after today,} she thought.

Monique watched as Quinn slid the stockinette up her right leg, over the knee, and to her
hip. As always, he took care not to touch her inappropriately. She liked the way the soft cotton
felt as it clung to her skin. He started wrapping the padding high on her thigh, and worked it
to the foot. She noticed that he put two extra layers at the knee and ankle, and that he took
care to keep the padding from wrinkling or bunching up, even unwrapping and rewrapping it in a
few places.

Before starting the fiberglass, I told Monique ``This is a little different than the
plaster, but mostly the same.''

As Quinn tore open and wet the first roll of fiberglass, Monique noticed that it had a
fruity smell. As he began to wrap her thigh, it felt pretty much the same as the plaster had. He
wrapped the first rolls from the top of the cast to just below the knee. He then folded the
stockinette and padding over at the top, and used another roll to anchor it, winding this roll
down to below the knee as well. The next rolls started just above the knee,, working down to the
ankle. From her reading, Monique now knew that casts need a little extra strength at the joints.
She noted that he was working the fiberglass smooth with each roll, where with the plaster; he
didn't start smoothing it until the cast was nearly done. By the time he anchored the
stockinette perfectly in line with the web of her small toe, she knew why: the cast was warm at
the thigh, and she could tell it was nearly set. This was a bit disappointing to her, as she
rather enjoyed the feel of his hands through the cast as he worked the plaster smooth. She had
also been hoping for a rubber heel on the cast- She'd been wanting to try walking on a cast, but
it didn't look like she would get that chance, at least not today.

After I had finished with Monique's cast, I set the stand under the calf to support it as it
finished drying, even though it was already feeling hard on the outside. As it dried, I picked
up the wrappers from the fiberglass rolls, and straightened up the casting room. After a few
minutes, I took my cast saw, spreaders and bandage scissors, and put them in a small overnight
bag. I then went to the other room, and retrieved my drawing supplies, and camera. As I put them
in the bag, I asked her: ``Are you ready?''

``Yes. We're taking the saw along?''

``Just in case.'' I told her. ``The truck has an AC inverter to run the saw if we need to
get you free while we're out.''

``Probably a good idea, but I'm getting a little used to wearing casts.'' Monique said with
a slight smile.

What's with the smile? I wondered to myself. I handed her the crutches and asked her ``Are
you ready?''

``Yes, I'm sort of interested in seeing how people react.''

What did she mean by \emph{that}?

I led her out the back door and to the garage. I opened the garage door for her and turned
on the light.

She stopped for a minute and looked over the Mustang and the Harley.

``Nice toys.'' She said. ``I guess you get paid pretty well, too. What year is that
Mustang?''

``1967 GT-500.'' I replied. ``Overindulgent plaything, but I couldn't resist it.''

She nodded. ``I'll bet. I don't suppose we could drive that today, could we?''

``Better to take the truck. I think you'd be more comfortable in it.''

``I guess so,'' she said. ``But I want a ride sometime.''

``I think we can arrange that.'' I helped her in, and then stashed her crutches and the bag
in the bed of the truck.

It took us almost an hour to get to the park. The park was over the state line, and far
enough away that the risk of running into anyone either of us knew was minimal. On the way, we
talked about several different subjects, mostly small talk. Once at the park, I got her
crutches, and helped her out of the truck. I was a bit excited. I was about to be seen in public
with a beautiful woman wearing a cast, and it was a total sham. I didn't really like her, and
her leg wasn't really broken. Anyway, here we go!

The park wasn't crowded by any means, but it was well-populated with the usual park crowd:
bicyclists, joggers, walkers, and playing children. We walked around for a while, and then
headed up the walk to a picnic table at the edge of the water to take a rest.

During the walk, Monique could feel her heart beating a bit faster than normal. She was
watching the people, and she noticed several of them looking at her. She was definitely
attracting attention with her cast, and she slowly came to realize- She liked it!

Sitting at the table, looking out over the stream, Monique surprised me with an idea.
``Wouldn't it be cool to go for a ride on your bike with me wearing a cast?''

The idea floored me. All I could think to say quickly was ``It would have to be a smaller
cast than that one.''

``Yes, but wouldn't it be great? Bikes get attention anyway, and the cast would make it more
so.''

I wondered for a moment who was the caster, here. ``So, you enjoy being the center of
attention?'' I asked.

``I'd never thought about it too much before, really. I know most men find me attractive,
and I've always gotten a lot of attention, but just being out today in this cast has really been
fun. I'm starting to think this odd little fetish we're playing out might not be as odd as I
originally thought. So, can we do the bike trip sometime?'' She said with a smile.

``I guess we probably could. Of course, I'll have to check.''

I took some pictures of her at the table, and then we walked a bit further to a small
monument. I took a picture of her in front of it, and decided to do the sketch there, as well.

After the sketch was finished, I showed it to her, and she nodded in approval. We walked
back to the truck, and on the ride home, she began asking questions about future sessions. She
mentioned the bike ride, and also wanted to know more about the larger casts, as well. She asked
about different casts, and I noticed that she was referring to them by their proper names:
shoulder spica, Minerva, and such. I could tell she'd been studying casts, but I wasn't sure
why. She might have been simply trying to understand what we were doing better. Of course, I
assumed it was probably because she was angling to get to the person behind the money. Then
again, I had to consider the possibility that she actually was enjoying this. The rest of the
ride home, and during the removal of the cast, I kept weighing these possibilities.

After I'd cut her out of the cast, she went on her way. I took the cast downstairs and put
it with the others, still thinking about the day, and her reactions.
