\chapter{Angie}
After just under four weeks of running my ad in Kicks, I certainly have to call it a
success. I have had more calls than I thought I would get. Thus far, I've had the two casting
sessions with local women, both of which seem to have gone very well. I have another one
scheduled for today, and I even have had a referral! I will be interviewing a woman tomorrow who
was referred to me by Diane. Although I don't hold out much hope for this one, as she is a bit
standoffish, it is still remarkable to be recommended by a model!

At any rate, my job at hand is to prepare for Angie. Angie is a stunning young woman who is
going to look fantastic in a cast. I'm going to place her in a fiberglass long arm cast, so I
set out the necessary supplies: Purple fiberglass in three and four inch widths, three inch
padding, and three inch stockinette.

Angie arrived just a few minutes before 3:00 p.m. I took her inside and showed her to the cast
room. She removed her t-shirt and denim shorts, revealing the white camisole and underwear she
had told me she would wear.

``How's this?'' she asked.

She looked fantastic. ``That looks great. Would you like something to drink before we get
started?''

``No, I'm fine. I'm ready whenever you are.''

``Alright, first things first.'' I went into my usual routine of showing her the money, then
placing it with an envelope, and leaving it with her clothes.

``Thanks,'' she said. ``That is going to come in very handy.''

``Actually, I thank you, Angie. I'm always in need of more models for my work. Some people
change their minds about being a model when they hear that I want them to wear a cast. Some
people just find it to be too strange, though it's really harmless. The man I do this for would
never want to see anyone actually injured, he simply likes the way a beautiful woman looks in a
cast.''

``Oh, it's definitely strange, but as you said, nobody is getting hurt, so I don't see anything
wrong with it.''

``Exactly. If you're ready, let's get started.''

``Okay.''

I took the stockinette and cut off a piece a bit longer than Angie's arm. I slid the stockinette
up her arm, letting it bunch up at her armpit and overhang the fingertips slightly. I cut a
small ``V'' in the area over her thumb, then helped her get her thumb through the cut.

I took a roll of padding, and began wrapping at her wrist. After a turn to anchor it, I worked
it past her thumb, and made two turns to pad her hand. It covered her fingers too much, but I
would be trimming it back later. I instructed Angie to hold her wrist straight, with the palm of
her hand turned upward, and her elbow at a ninety degree bend. I continued up her arm,
overlapping each turn by half. This gave an almost completely uniform two layers of padding. The
first roll was not quite enough to get as high as I wanted the cast, so I had to start a second
roll. When I got to her armpit, I tore off the remainder of the roll, and set it aside. I
anchored the end of the padding with a piece of tape, and went to fill my bucket with warm
water.

When I returned, I checked to make sure Angie was still OK, and if she needed anything before we
continued.

``No, I'm fine. I'm just watching you work.''

``In that case, I'll continue.''

I took a plastic dropcloth and wrapped it loosely around her body, taping the ends together over
her left shoulder.

``This will keep the fiberglass from getting on your clothing or skin,'' I said.

I tore open a roll of three inch purple fiberglass and dipped it in the warm water. After the
bubbles stopped I wrung it out, and began wrapping Angie's arm at the wrist. I worked it over
her wrist and hand in a figure eight fashion, folding it into a ``Z'' where it passed between
her thumb and forefinger. After her wrist and hand were encased in four layers of fiberglass, I
finished the roll by working up her forearm. I then took my scissors and cut the excess padding
away from her fingers, leaving just a half inch protruding. I then cut the stockinette, leaving
enough to be folded over and anchored. I trimmed the stockinette and padding around the thumb so
that it, too could be anchored with the second roll of three inch fiberglass. I finished off
this roll by, once again, working toward the elbow.

The first roll of four inch fiberglass started at mid forearm, and I worked it all the way up to
her upper arm. Another roll of four inch followed, and by this time, I had the cast to its
desired height, which was just below the armpit. I folded over the stockinette and padding at
the top of the cast, And anchored it with a final roll of four inch fiberglass that continued
downward.

I pulled off my gloves, and tossed them into the trash.

``There it is, all finished. It's probably feeling pretty warm by now.''

``Yes, it has been for a bit- ever since you started the second roll.''

``That's just the chemical reaction of the fiberglass hardening. It won't get any hotter than it
is right now.''

``How long until it is completely dry?''

``It takes about thirty minutes for it to completely set up, but we don't need to wait quite
that long. After another ten minutes, we'll be ready to get started with the photos and
sketching. Would you like something to drink in the meantime?''

``Sure. Do you have anything diet?''

``That's all I drink,'' I said with a smile. ``Hang on.''

I went to get us each a soda, when I returned, I noticed her carefully examining her cast.

``So, what do you think of my work?''

``It looks fine to me,'' she said. ``I don't think it looks any different than ones I've seen
that were real.''

``It's made the same way that medical professionals make them. Let's see how it is drying.''

I examined the cast. It was still warm on the exterior. I wiped away the excess surface moisture
with a cloth. The stickiness from the resin was gone everywhere except the very top.

``It's almost dry. Let's give it a few more minutes, and we'll move to the other room.''

After we had finished our drinks, I removed the dropcloth that I had placed over her. She sat
there, in her skimpy clothing and huge arm cast, and I must say- she was breathtaking!

I retrieved my camera, and took a few photos of her sitting on the casting table. We then moved
to the studio, where I had her take a seat on the couch. After I had snapped several more photos
of her, I set her in the pose I wanted to sketch. I drew her from the right side, sitting in a
relaxed position. I made the cast totally the foreground of the drawing.

After I had finished, I showed her the sketch.

``Wow, that's really good. It certainly looks like me.''

``Thank you very much. I take quite a bit of pride in this,'' I said. ``Are you ready to get out
of that thing?''

She had a bit of a strange look on her face as she answered.

``Yes, I am, but it would be sort of interesting to wear this to classes for a day or so.''

``If you did that, a lot of people would ask questions. Even worse, if you had it one day, then
it was gone, they'd REALLY ask!''

``Yes, I guess they would, wouldn't they? Let's go ahead and take it off.''

I led her back to the casting room, and retrieved my Stryker saw and bandage scissors. After ten
minutes, her arm was free once again, and she put her clothes back on. As she slipped the money
into her pocket, she thanked me.

``No, Angie, it is I who thank you. You've been great to work with, and if you'd like, we can
certainly do this again.''

``I think I might like to. How about if I give you a call about it?''

``That's fine. If you decide against it, that's fine, as well. I've enjoyed working with you.''

``Thank you, it was nice working with you, too. I'd better be going, now. Goodbye.''

``Goodbye.''

After she left, I took the cut off cast, and took it to the basement and placed it with the
others. I returned to the casting room to clean up.
