\chapter{~}
Tuesday had been eventful. I had met the most exciting woman I had seen in a long time,
maybe ever. She was considering being a cast model for me. I could not deny to myself how much I
hoped she would accept. Nor was I kidding myself that possibly I wanted more than just to cast
her.

I had also established one regular cast model, even if it was Monique. Besides, Monique was
very beautiful, despite her personality. I tried to figure her out. I wondered why she was so
eager to accept the higher involvement casting without even asking about the increased pay. I
would have figured she would be all over that. It didn't make any sense at all until it occurred
to me that she was likely angling to get past me, and straight to the fictitious ``money man.''
By appearing enthusiastic maybe she hoped to get more attention, maybe have the rich sponsor
want to meet her, and then let her physical attributes work their charm. Ugh, as ugly as it
sounded, that had to be it. Well, maybe I'll work with her until I establish a couple more
models, then cut her loose. I'll tell her that the man in charge has no further interest in
seeing her casted. That will put her in her place. But for now, casting Monique is a lot better
than casting nobody, so I'll roll with it for a while.

\begin{thought}
Monique still could hardly believe what she'd heard the day before. More casts? Bigger
casts? Public?! This was too good to be true! What Quinn proposed was exactly what she had been
wanting! It was a shame that Quinn wasn't more into this himself. Though it was just a job to
him, it was a life she was liking more and more all the time. It was probably best that he
wasn't truly a ``caster,'' though. She was having enough trouble keeping up her normally iron
clad self control anyway, if he was really into it, she might end up throwing herself at him and
messing everything up. She was obviously letting her newfound fascination with wearing casts get
the best of her emotions. She reminded herself: ``Remember, Monique- this is just a job to
Quinn, and he thinks it's just a job to you, too.''
\end{thought}

My phone rang, and to my pleasant surprise, it was Erin.

``Hello, Quinn. If the job is still open, I'll take it.''

I was ecstatic, but hid it. ``It is still open.'' I told her. ``I'm glad you've accepted. I
think I'll enjoy working with you.''

``Well, I'll be honest with you, this wierds me out, but I need to make some money. I can't
promise that I'll do it any longer than it takes for my leg to heal. I have a good job, and
they're holding it for me, but I need to pay my rent in the meantime.''

``I understand,'' I said. Her words disappointed me a bit, but they were understandable.
Besides, even if it was only once, I wanted to cast her! I hoped that maybe she would find it
not so bad when it was temporary, and not accompanied by pain. Sure, that was a longshot, but
some women actually enjoyed being casted, though I doubted the likelihood that I'd ever meet
one.

``When do we get started?'' she asked.

``How about Monday? In fact, we could make that our normal day.''

``You said I'd be paid in cash the day of the work, right?''

``Yes''

``Then Monday will be fine. And if I decide to do this any more after the first time, we can
always work on Mondays. My schedule is really pretty open.'' She said.

``Also, we can work around conflict, if we need to,'' I added.

``Ok, we'll do this Monday. I'll try it, and then decide if I want to do it again. Is that
OK?''

``Absolutely, but only if you're comfortable.''

``Thanks. Oh, what should I wear? Besides my cast, that is.''

I gave her a rough outline of the type of clothing I wanted, and she said she had some
different things that might work, and she'd bring a selection with her. We said our good-byes,
and I as faced with a pleasant dilemma: how did I want to cast her? I could think of a lot of
ways I WANTED to, but I didn't want to overwhelm her, and scare her away. I wanted to cast her
more than once.

While I pondered how to ``dress'' Erin, I decided to call Monique, and get her scheduled,
too. I told her I'd like to cast her on Fridays, starting a week from the one coming. She
sounded eager when she accepted.

``Sure, Quinn. What sort of cast will I get this time?''

``Well, I don't know yet. I'll talk to the boss, and see if there's anything particular he'd
like to see you in.''

Her next statement floored me:

``Well, if he doesn't have anything in mind, I can help you decide if you need me to.''
